
%-------------------------------------------------------------------------
\section{Broader Impact}\label{sec:impact}
%-------------------------------------------------------------------------

\paragraph{Broader Applications} This project will benefit the interface design and evaluation of a broad range of complex tele-robotic systems, including mobile manipulator robots, humanoids, multi-arm manipulator system, and multi-agent robots. The proposed human performance metrics can be generally applied to evaluate the robot operation skill for industrial, medical, social and in-home assistance, construction, space and military tasks. It also provides a framework for evaluating the skill development of general-purpose motor tasks and motor recovery in rehabilitation.  

\paragraph{Research-Education Synergy} This project will synergize research effort with graduate and undergraduate education in robotics engineering on human-robot interaction and industrial robotics at WPI. This project will support one PhD student as research assistant, to work on the experimental study on teleoperation interface comparison and teleoperation skill progression. It will involve a second graduate student for 3-month summer research to assist data analysis and improve the robot teleoperation interface with multi-model cognitive augmentation. This project will provide hand-on projects to a graduate course (RBE 595 --- Synergy of Human and Robotic System) offered to students with robotics engineering program, and a undergraduate courses (RBE/ME/MFE 4815 --- Industrial Robotics) offer to students with robotics, mechanical and manufacturing engineering. It will also offer project and platform to inter-disciplinary major qualifying project (MQP) for senior undergraduate student with the college of engineering at WPI. Through this MQP we will develop a 3D printed, customizable robot teleoperation interface for intuitive control of mobile manipulator robots. The MQP project outcome will be shared as open-source CAD model and ROS-compatible software package. This project will engage K-12 students through First Robotics and general public in the annually Touch Tomorrow event at WPI.

\paragraph{Potential Future Work} The proposed project is primarily concerned of teleoperating mobile humanoid robots to perform low-precision motion coordination tasks. Future work will be extended to the teleoperation of multi-robot system for high-precision tasks (e.g., surgery and cable-tie tasks), and of large number of robots (e.g., swarm robots). The implementation and system evaluation can be conducted on the multi-arm surgical robot platform available at WPI AIM lab, swarm robot system available at WPI NEST lab, and industrial robot platform available at NIST research labs. Our future work will extend framework for motion and task modeling to encompass the scenario of multi-lateral teleoperation --- which enable multiple teleoperators to (simultaneously) control different components of a robotic system.  We will also develop robot control interface that provides intelligent assistance that automate the task components different for direct teleoperation control, and shift the control between human teleoperator and intelligent tele-operated robot based human skill and fatigue level. 
