\pagebreak

\begin{center}
	{\Large \bf Supplementary Documents --- Human Subjects Protection}\\
%     \vspace{4pt}
% 	\renewcommand{\baselinestretch}{1}
%    	{\large PI: Zhi Li (Worcester Polytechnic Institute)\\
%     Co-PI: Brian Ziebart (University of Illinois at Chicago), Jie Fu (Worcester Polytechnic Institute)}
   	% \vspace{4pt}
    % {\large Worcester Polytechnic Institute}
\end{center}

\vspace{0.5em}

Both the University of Illinois at Chicago and Worcester Polytechnic Institute will have their Institutional Review Board (IRB) review all research involving the use of human subjects. All PIs are familiar with IRB policies, including fulfilling the required continuing training in human subjects protection.

We will submit an IRB protocol to cover the collection of human demonstration and the user study for system evaluation. We foresee that the IRB will review the protocol under expedited procedure, since it is minimal risk. Our study aims to demonstrate the system usability and will be performed in simulated patient room. We will have healthy subjects to play the roles of patients. No real patients will be involved.

%-------------------------------------------------------------------------
\section{Data collection}\label{sec:data}
%-------------------------------------------------------------------------

Our experiment will record robot and human motions in robot-mediated nursing tasks, using cameras, a motion capture system, and robot sensors. We will record full body motion and audio of the participants and collect questionnaires to evaluate user experience. All the data will be de-identified for privacy and confidentiality. 

%-------------------------------------------------------------------------
\section{Potential Risks}\label{sec:risk}
%-------------------------------------------------------------------------
The risks in robot teleoperation and interaction are minimized. The humanoid robot involved in this experiment is the Baxter robot from Rethink Robotics. This robot is designed to work safely and efficiently alongside people. In particular, it has safety and compliance features that slow or stop upon inadvertent contact, which allows it to work collaboratively or to be co-located with an operator in close proximity. The Baxter robot has a wide array of innovative sensors, and an emergency stop (E-stop) function to ensure safety, which will be carefully administrated by a trained experimenter. In the event of a power loss or an E-stop, the robot slowly comes to rest. Baxter’s arms, which will physically interact with the subjects, weigh less than 20 kg, are fully covered in compliant plastic, and use protective foam at key joints. Baxter can recognize human proximity with its $360^\circ$ sonar system, which signals its awareness of any detected nearby people. The Baxter robot meets the applicable parts of ISO 10218-1. 

Given the intrinsically safe robot platform, the potential risk of this study may include: (1) physical and mental fatigue in robot teleoperation and interaction, (2) the confidentiality of collected data that may reveal the participant identities. 

%-------------------------------------------------------------------------
\section{Recruitment and informed consent}\label{sec:consent}
%-------------------------------------------------------------------------
% PM: IIRC normal age of consent is 18? Why choose 21?
We plan to recruit 20-30 adults over age 18 who are capable of providing consent. The on-site research assistant will be available to discuss the risks and benefits of the study and answer any questions. The following will be explained: (1) purpose; (2) financial compensation for completing the study; (3) types of data collected; (4) virtual and human coach interventions; (5) measures to ensure confidentiality of data collected; and (6) timeline. Regarding data collection, subjects will be made aware of the methodology, including all the data being recorded. They will also be informed that, if they provide separate consent, their de-identified data will be released to other research groups at the end of the project.
% PM: I'm not sure why you're sending text messages to participants, and nothing you've mentioned so far suggests this? Maybe just get rid of this sentence?


%\subsection*{Inclusion of women, minorities and children}
\paragraph{Inclusion of women, minorities and children.}
We plan to recruit only adults over age 18 who are capable of providing consent. For the present study, neither minors nor persons with without motor, vision, hearing, cognitive impairments will be recruited. We will recruit women and minorities to ensure that our human subjects are representative of the general population and of nursing professionals. 

%\subsection*{Planned procedures to protect against or minimize potential risks}

%-------------------------------------------------------------------------
\section{Planned procedures to protect against or minimize potential risks}\label{sec:protection}
%-------------------------------------------------------------------------
To protect against the minimal risks involved in robot teleoperation and interaction, the experiment trials will be broken into several exercises expected to take no more than 20 minutes each, and subjects may take breaks between exercises. The experiment will only continue if the subject feels comfortable to continue. The subject can ask to terminate the experiment at any time he/she wants. If any emergency happens, the experiment administrator will call 911.

As concerns privacy and confidentiality, we will keep de-identified data on password-locked computers, including one of the servers in PI Ziebart's laboratory in the Science and Engineering Laboratories building of UIC, and one of the servers in PI Li's laboratory in the Robotics Engineering Program at WPI. Both laboratories are locked and only the PIs and their graduate assistants have access. The data will be accessible only to the PIs and their graduate assistants. The data will be stored on different servers because software tools that are needed to process the data are not available on every server, e.g. because of licensing issues.